\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[]{rss}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Resume},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=Blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\name{Lukasz Tymoszczuk}
\address{\\[-9pt] lukas@codeily.com | lukastymo.com}
\begin{resume}

I'm a Scala / Data Engineer with over eleven years' experience. I
inspire and help teams in being productive. I love mathematics,
algorithms and problem-solving. I'm a founder of scalaworkshop.com.

I'm goal oriented, proactive and able to work remotely, with outstanding
communications skills.

My business experience: Legal (ISDA, initial margin documentation),
Machine Learning (Apache Spark, Scala, Python, Docker), Finance and
Banking (Risk Management FRTB, MIFID, Basel), Energy industry (Energy
price forecasting, IoT), Public sector (Automatic recruitment system),
Aviation.

My after-work activities:

\begin{itemize}
\tightlist
\item
  My homepage and blog: \href{https://lukastymo.com}{lukastymo.com}
\item
  Scala course: \href{https://scalaworkshop.com}{scalaworkshop.com}
\item
  \href{https://stackoverflow.com/users/574799/smas}{stackoverflow.com/users/574799/smas}
  (top 2\%)
\item
  \href{https://codeforces.com/profile/smas}{codeforces.com/profile/smas}
\end{itemize}

Technical experience:

\begin{itemize}
\tightlist
\item
  Scala (Functional Programming), Java (SOLID, OO), JVM
\item
  Big Data: Apache Spark, HDFS, Apache Hive, ETL, SQL, Docker
\item
  Machine Learning, Python / Jupyter Notebook
\item
  DevOps \& Cloud: AWS, Ansible, Terraform, Grafana, Docker and
  Kubernetese, ELK
\item
  Distributed Systems: Akka, Microservices, NoSQL, The Twelve-Factor App
\item
  Agile Development practices: CI/CD, TDD, Pair Programming, Code Review
\end{itemize}

\hypertarget{education}{%
\subsubsection{Education}\label{education}}

\begin{itemize}
\tightlist
\item
  M.S., MBA, University of Illinois Urbana-Champaign, 2019 - present,
  USA
\item
  M.S., Computer Science, Jagiellonian University, 2005 - 2010, Krakow,
  Poland
\end{itemize}

\hypertarget{senior-scala-developer-contract}{%
\subsubsection{Senior Scala Developer
(contract)}\label{senior-scala-developer-contract}}

\emph{Linklaters \textbar{} Nakhoda} November 2018 -- December 2019,
London, UK

\begin{itemize}
\tightlist
\item
  We worked on the new way of negotiating the International Swaps and
  Derivatives Association (ISDA) documentation.
  \href{https://nakhoda.ai}{nakhoda.ai}
\end{itemize}

Tech stack and activities:

\begin{itemize}
\tightlist
\item
  Functional Scala, Cats, Monix Tasks, Doobie
\item
  PostgreSQL
\item
  TDD, Automated tests
\item
  Kubernetes, Docker, On-premise Cloud
\item
  REST, API versioning, Swagger, Database migration
\item
  I worked closely with our DevOps team as a part of the release rota
  (releases and hotfixes)
\end{itemize}

\hypertarget{data-engineer-contract}{%
\subsubsection{Data Engineer (contract)}\label{data-engineer-contract}}

\emph{Royal Mail \textbar{} GBI} May 2018 -- November 2018, London, UK

\begin{itemize}
\item
  I was part of Data Engineering team. I developed Data Platform and
  data algorithms on it which transformed the whole business and allowed
  releasing multiple great products. I advised and recommended best
  practices in Scala, Agile and Software Development, Architecture.
\item
  I implemented opt-1, opt-2 and opt-3 heuristic to solve VRP (Vehicle
  routing problem). This algorithm was essential for Royal Mail
  business, as it is unpractical to solve this task manually. Thanks to
  this algorithm another project ``Late Arrival Packages'' was able to
  kick off.
\item
  I developed parcel delivery project which processed terabytes of data
  in a few hours. I was responsible for productionizing (porting from
  POC Python code to Scala) and implemented new features for Machine
  Learning modules: Train, Test, Post-process and Formatter. This
  project was able to predict 90\% of all packages UK-wide with 2-hour
  precision.
\end{itemize}

Tech stack:

\begin{itemize}
\tightlist
\item
  Scala (main production language), Python (PoC)
\item
  Apache Spark (Spark SQL), Yarn, HDFS, Linux, Apache Zeppelin,
\item
  TDD, Kubernetes, Docker, Akka-HTTP, MongoDB, Cats
\item
  On-premise Cloud
\item
  REST, Swagger, Gatling
\end{itemize}

\hypertarget{big-data-developer-contract}{%
\subsubsection{Big Data Developer
(contract)}\label{big-data-developer-contract}}

\emph{IHS Markit \textbar{} Risk Factor Utility (FRTB)} September 2017
-- May 2018, London, UK

\begin{itemize}
\item
  I productionized Spark application on AWS (S3, EC2, EMR) with strong
  automatization requirement via Ansible and CloudFormation. Due to this
  change deployment across environments was consistent and automated, so
  everybody on the team could do this by clicking one button in Jenkins.
\item
  I was part of the team which implemented very popular, and in-demand
  project required transforming the significant amount of raw market
  data into FRTB-compliant risk factors and scenarios by using DSL
  language for risk modelling.
\item
  I helped developing functional Scala project, which the main module
  was a custom DSL language used by Quants. Thanks to this feature, our
  quants were able to produce FRTB solutions presented for multiple
  banks.
\end{itemize}

Tech stack:

\begin{itemize}
\tightlist
\item
  Scala, Cats, Monix Tasks
\item
  Apache Spark, Hadoop, Cassandra
\item
  AWS (EC2, S3), Cloud Computing, EMR, Yarn
\item
  Apache Zeppelin, Big Data, Helping BAs with notebooks written in
  Python
\item
  CI / CD, Ansible, Git workflow
\item
  TDD, Code review, Scrum team
\item
  REST, Swagger
\item
  Agile: Scrum
\end{itemize}

\hypertarget{software-engineer-contract}{%
\subsubsection{Software Engineer
(contract)}\label{software-engineer-contract}}

\emph{OVO Energy \textbar{} vCharge} April 2017 -- September 2017,
London, UK

\begin{itemize}
\item
  vCharge was a startup acquired by Ovo Energy. The idea was to control
  storage heaters installed in people homes. I worked with the owner,
  who was located in the US (\textasciitilde{} daily one-to-one online
  meetings). I had a high impact on stakeholders. Throughout a couple of
  months, I was the only Scala developer.
\item
  I built a module to forecasting Energy prices using the Dijkstra
  algorithm and mathematical model created by Data Scientists. It
  allowed buying energy cheaper and ``store'' in the customers' storage
  heaters.
\end{itemize}

Tech Stack:

\begin{itemize}
\tightlist
\item
  Scala, Akka, Play Framework, Lagom Framework
\item
  CQRS / Event Sourcing, Cassandra
\item
  Python (PoC)
\item
  Microservices
\item
  ScalaTest, Property-based testing
\end{itemize}

\hypertarget{scala-consultant-contract}{%
\subsubsection{Scala Consultant
(contract)}\label{scala-consultant-contract}}

\emph{Civil Service Resourcing (Valtech) \textbar{} Faststream,
Fasttrack} February 2016 -- April 2017, London, UK

\begin{itemize}
\tightlist
\item
  I developed an auto-grader module inside the web-based application
  deployed on HMRC's Tax Platform. The module allowed to assess and send
  emails to 120,000 candidates in a day-scale vs month-scale in the
  legacy system.
\end{itemize}

Tech stack:

\begin{itemize}
\tightlist
\item
  Scala and functional design
\item
  Play framework, RESTful API, MongoDB
\item
  Microservices, Kibana, Grafana
\item
  Cucumber, ScalaTest, Property-based testing
\end{itemize}

\hypertarget{senior-software-engineer}{%
\subsubsection{Senior Software
Engineer}\label{senior-software-engineer}}

\emph{Monitise \textbar{} FinKit platform, Matm} August 2013 -- February
2016, London, UK

\begin{itemize}
\tightlist
\item
  After a year of developing OSGI, Java platform for multiple financial
  institutions I was moved to brand new cloud platform with Scala, Akka,
  Microservice architectures: FinKit.
\end{itemize}

Tech stack:

\begin{itemize}
\tightlist
\item
  Scala, Akka
\item
  REST: Spray, Swagger (generator)
\item
  IBM Bluemix, NoSQL: Cloudant, AMQP protocol
\item
  Java 6 / 7, Apache Camel
\item
  Modularization: OSGi, Messaging: JMS
\item
  REST, SOAP, SOA
\item
  TDD, BDD, Continuous Delivery, Continuous Integration
\end{itemize}

\hypertarget{full-stack-java-developer}{%
\subsubsection{Full stack Java
Developer}\label{full-stack-java-developer}}

\emph{Sabre Holdings} November 2010 -- August 2013, Krakow, Poland

\hypertarget{full-stack-java-developer-1}{%
\subsubsection{Full stack Java
Developer}\label{full-stack-java-developer-1}}

\emph{ComArch} June 2008 -- November 2010, Krakow, Poland

\end{resume}

\end{document}
